Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2016-01-16 WSSSPE3/report/wg_main_eng_design.tex
Update wg_main_eng_design.tex
Minor update

>>>>

It was suggested that at the very minimum, the genetic building blocks of [technically] sustainable software should address two core quality attributes:
\begin{itemize}
\item Extensibility: the software’s ability to be extended and the level of effort required to implement the extension;
\item Maintainability: the effort required to locate and fix an error in operational software.
\end{itemize}
These fundamental building blocks could then be extended to include other quality attributes such as portability, resuability, scalability, usability, and energy efficiency etc. Nevertheless, this raises the question of what metrics and measures are suitable to demonstrate the sustainability of the software. This raised the question, What do the principles mean for scientific and computational software? Similalry, how do the principles relate to non-functional requirements? In addition, what do the five dimensions of sustainability mean for scientific software i.e. environmental, economic, social, techincal and individual?
